A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-04 manuscript.Rmd
explain pull and push close #21
explain .gitignore closes #9
add a reference for learning Git
closes #23

<!--I am troubled by how we should recommend to learn Git-->
Git can be challenging to learn because we are used to learning alone, and Git is best learned with others.
We recommend finding a partner to attend an online lecture or workshop to learn the ins and outs of Git.

@@

>>>>

<!--I am troubled by how we should recommend to learn Git-->
Git can be challenging to learn, because it requires a rather complex mental model.
However, there is a subsets of commands which we present here and in the section on [GitHub] (commit, push, pull) which enable you to utilize Git for simple version control.
There are many tutorials on learning Git and @vuorreCuratingResearchAssets2018 provide a good starting point.
However Git is designed for collaboration, we therefore recommend finding a partner to attend an online lecture or workshop to learn the ins and outs of Git.

@@

After you have initially uploaded your repository to GitHub, you need to regularly synchronize your local copy and GitHub.
Uploading commits to GitHub is called "push":

```r
gert::git_push()
```

Downloading changes, e.g. from your collaborators is called "pull".

```r
gert::git_pull()
```
